\section{TPO 01 Passage 3}

\subsection{Words}

\begin{tabular}{lll}
    tropic & n. & 热带 \\
    deform & v. & 变形 \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q14. Summary
    \end{qst}

    \begin{chc}
        A.Birch is one of the few species of tree that can survive in the extreme environments of the upper timberline.

        B.There is no agreement among scientists as to exactly why plant growth is sharply different above and below the upper timberline.

        C.The temperature at the upper timberline is probably more important in preventing tree growth than factors such as the amount of snowfall or the force of winds.

        D.The geographical location of an upper timberline has an impact on both the types of trees found there and their physical characteristics.

        E.High levels of ultraviolet light most likely play a greater role in determining tree growth at the upper timberline than do grazing animals such as the ibex.

        F.Despite being adjacent to the timberline, the alpine tundra is an area where certain kinds of low trees can endure high winds and very low temperatures.
    \end{chc}

    \begin{nlz}
        A 选项提到了具体的树种桦树，明显是一个细节选项，A 选项不选；

        B 选项对应第四段首句，B 选项正确；

        由第四自然段大意及第四自然段的“Probably the most important environmental factor is temperature”可得 C 选项正确；

        D 选项对应第二段的第三句和第三段的首句，D 选项正确；

        E 选项中，原文没有将两者进行比较，则 E 选项不正确；

        F 选项中，虽然文章倒数第二自然段提到了紧挨着树带界线，苔原上都是矮灌木、草本植物和牧草，但是，文章中并没有直接介绍说这些低矮的树木能够忍受大风和低温。
    \end{nlz}
\end{blk}
