\section{TPO 30 Passage 02}

\subsection{Words}

\begin{tabular}{lll}
    enliven     & v.   & 使...更有趣             \\
    increment   & n.   & 增量；增加；增值            \\
    obscure     & adj. & 无名的；费解的，晦涩的;模糊的，朦胧的 \\
    punctuate   & v.   & 加标点；不断打断            \\
    burst       & v.   & 心情迫切；（使）迸裂；（使）爆炸    \\
    equilibrium & n.   & 平衡；均衡               \\
    lengthy     & adj. & 漫长的，冗长的             \\
    exhaustive  & adj. & 详尽的                 \\
\end{tabular}

\subsection{Collocation}

\begin{tabular}{ll}
    give rise to & 引起，导致 \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q2. According to paragraph 1, all of the following are true EXCEPT:
    \end{qst}

    \begin{chc}
        A. Darwin saw evolutionary change as happening slowly and gradually.

        B. Gaps in the fossil record were used to explain why it is difficult to see continuous small changes in the evolution of species.

        C. Darwin’s evolutionary thesis was \textbf{rejected} because small changes could not be observed in the evolutionary record.

        D. By the early twentieth century, most biologists believed that gradualism explained evolutionary change.
    \end{chc}

    \begin{psgq}
        A heated debate has enlivened recent studies of evolution. Darwin’s original thesis, and the viewpoint supported by evolutionary gradualists, is that \textbf{species change continuously but slowly and in small increments}\textsubscript{A}. Such changes are all but invisible over the short time scale of modern observations, and, it is argued, \textbf{they are usually obscured by innumerable gaps in the imperfect fossil record}\textsubscript{B}. Gradualism, with its stress on the slow pace of change, is a comforting position, repeated over and over again in generations of textbooks. \textbf{By the early twentieth century, the question about the rate of evolution had been answered in favor of gradualism to most biologists’ satisfaction.}\textsubscript{D}
    \end{psgq}

    \begin{nlz}
        正确答案C。A答案对应第一段第二句， B对应第一段第三句，D对应一段最后一句。C与原文冲突，原文一直在说darwin理论被人们广泛接受。
    \end{nlz}
\end{blk}
