\section{TPO 38 Passage 03}

\subsection{Words}

\begin{tabular}{lll}
    perpetuate & v. & 使永存；使人记住不忘\\
    scenario & n. & 情节；剧本；方案\\
    alongside & adv.prep. & 靠着边；与…放在一起比较；与…一起，与…一道\\
    acre & n. & 英亩；土地，地产\\
    soybean & n. & 大豆\\
    canola & n. & 油菜\\
    noxious & adj. & 有害的；有毒的；败坏道德的；讨厌的\\
    herbicide & n. & 灭草剂\\
    caterpillar & n. & 毛虫\\
    weed & n. & 杂草\\
    refuge & n.v. & 避难；避难所；庇护；给予…庇护；接纳…避难\\
    integrate & v. & 使结合成为整体；(使)融入\\
\end{tabular}

\subsection{Collocation}

\begin{tabular}{ll}
    attempt to & 以期; 试图\\
\end{tabular}

\newpage

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q8. Why does the author mention “\textbf{mustard weed species}” in the discussion of plants that hybridize?
    \end{qst}

    \begin{chc}
        A. To give an example of a weed that may become resistant to glyphosate due to hybridizing with a transgenic plant
    \end{chc}

    \begin{psgq}
        In this way, \textbf{the resistant gene can make its way into the weed population}. If this happens, a farmer can no longer use glyphosate, for example, to kill those weeds. This scenario is not likely to occur in many instances because there are no weedy relatives growing near the crop plant. However, in some cases, it may become a serious problem. \textbf{For example}, canola readily hybridizes with mustard weed species and could transfer its herbicide-resistant genes to those weeds.
    \end{psgq}

    \begin{nlz}
        例如canola这种作物就可以与mustard这种杂草杂交，把它的抗除草剂基因传给这种杂草。所以作者在这里的意思是举例杂交可以使得杂草具有抗除草剂的基因。
    \end{nlz}
\end{blk}

\begin{blk}
    \begin{qst}
        Q10. Which of the sentences below best expresses the essential information in the \textbf{highlighted sentence} in the passage? Incorrect choices change the meaning in important ways or leave out essential information.
    \end{qst}

    \begin{chc}
        C. Transgenic crop plants may be used in place of other, more sustainable agricultural practices, and this is perhaps their biggest disadvantage.

        D. Perhaps the most serious concern about the transgenic crop plants currently in use is the possibility that they may not be sustainable over the long run.
    \end{chc}

    \begin{psgq}
        Perhaps the most serious concern about the transgenic crop plants currently in use \textbf{is that} [they encourage farmers to move farther away from \textbf{sustainable agricultural farming practices}], (\textbf{meaning} ones that allow natural resources to continually regenerate over the long run.)
    \end{psgq}

    \begin{nlz}
        也许转基因作物带来的最严重问题是，它让农民开始放弃可持续性的耕作方式，放弃了那种可以让自然资源在长期自己再生的那种耕作方式。选项D指的是作物本身不可持续，逻辑错误。
    \end{nlz}
\end{blk}

\newpage