\section{TPO 39 Passage 01}

\subsection{Words}

\begin{tabular}{lll}
    hoard        & n.v.     & (钱财、食物或其他珍贵物品的)储藏, 积存  \\
    damp         & n.v.adj. & 潮湿；使潮湿；潮湿的             \\
    clay         & n.       & 泥土                     \\
    wedge        & n.v.     & 楔子；楔形物；楔入；挤进；楔住        \\
    reckon       & vt.      & 猜想；估计                  \\
    inscribe     & v.       & 题写；题献；铭记；雕             \\
    transaction  & n.       & 交易                     \\
    scribe       & n.       & (印刷术发明之前的)抄写员, 抄书吏     \\
    confer       & v.       & 授予；给予                  \\
    rub          & v.       & 擦；摩擦；惹怒                \\
    foremost     & adj.     & 最著名的，最重要的；最好的；主要的      \\
    ordeal       & n.       & 痛苦的经验；严酷的考验；折磨         \\
    epic         & n.adj.   & 史诗；叙事诗；史诗般的作品；史诗的，叙事诗的 \\
    calligrapher & n.       & 书法家                    \\
    shuffle      & n.v.     & 遗漏；改变顺序                \\
\end{tabular}

\subsection{Collocation}

\begin{tabular}{ll}
    be fit for & 适合于 \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q1. According to paragraph 1, \textbf{the name of the earliest form of writing reflects the fact that} this writing was
    \end{qst}

    \begin{chc}
        A.inscribed on damp materials

        C.made with a wedge-shaped stick
    \end{chc}

    \begin{psgq}
        Scholars agree that writing originated somewhere in the Middle East, probably Mesopotamia, around the fourth millennium B.C.E. It is from the great libraries and word-hoards of these ancient lands that the first texts emerged. They were written on damp clay tablets with a wedged (or V-shaped) stick; \textbf{since the Latin word for wedge is cunea, the texts are called cuneiform}\textsuperscript{C}. The clay tablets usually were not fired; sun drying was probably reckoned enough to preserve the text for as long as it was being used. Fortunately, however, many tablets survived because they were accidentally fired when the buildings they were stored in burned.
    \end{psgq}

    \begin{nlz}
        A选项正确但是不符合题目the name reflects
    \end{nlz}
\end{blk}

\begin{blk}
    \begin{qst}
        Q11. Which of the sentences below best expresses the essential information in the highlighted sentence in the passage? Incorrect choices change the meaning in important ways or leave out essential information.
    \end{qst}

    \begin{chc}
        B. The symbols for individual words were sometimes moved around in a text, regardless of these words’ meaning and sound, to make the text more beautiful.

        C. The glyphs used as symbols for individual words in texts were sometimes chosen more for their beauty than for their connection to sound or sense.
    \end{chc}

    \begin{psgq}
        Egyptologists have noticed that the glyphs that constitute individual words were sometimes shuffled \textbf{to make} the text more pleasing to the eye with little regard for sound or sense.
    \end{psgq}

    \begin{nlz}
        埃及古物学者注意到由单个文字组成的雕文有时候会被弄乱以让这些文字看起来更好，而不管这样做会不会影响发音或者意思。C没有提到打乱，也没有提到目的关系。
    \end{nlz}
\end{blk}
