\section{TPO 3 Passage 1}

\subsection{Words}

\begin{tabular}{lll}
    plumb   & v.   & 给…装水管       \\
    arduous & adj. & 艰难的，艰巨的；费力的 \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q7.According to paragraph 4, which of the following is true about materials used in the construction of buildings?
    \end{qst}

    \begin{chc}
        A. Because new building materials are hard to find, construction techniques have changed very little from past generations.

        B. The availability of suitable building materials no longer limits the types of structures that may be built.

        C. The primary building materials that are available today are wood, stone, and brick.

        D. Architects in earlier times did not have enough building materials to enclose large spaces.
    \end{chc}

    \begin{psgq}
        Even development in architecture has been the result of major technological changes. Materials and methods of construction are integral parts of the design of architecture structures. In earlier times it was necessary to design structural systems suitable for the materials that were available, such as wood, stone, brick. Today technology has progressed to the point where it is possible to invent new building materials to suit the type of structure desired. Enormous changes in materials and techniques of construction within the last few generations have made it possible to enclose space with much greater ease and speed and with a minimum of material. Progress in this area can be measured by the difference in weight between buildings built now and those of comparable size built one hundred years ago.
    \end{psgq}

    \begin{nlz}
        B 整段大量篇幅在讨论 building material，建议用排除法。A 的 new building material 定位到第四句，但是 A 选项的 hard to find 明显和这句话矛盾，错误；同样 B 选项也定位到这一句，no long limits 和这句话吻合，正确，选 B: Today technology has progressed to the point where it is possible to invent new building materials to suit the type of structure desired. C 的三种材料定位到第三句的列举部分，但很明显，他们应该是以前的主要建筑材料，不是现在。In earlier times it was necessary to design structural systems suitable for the materials that were available, such as wood, stone, brick. D 没说选项在原文没有提及，看上去长得像倒数第二句，但意思不同。
    \end{nlz}
\end{blk}
