\section{TPO 3 Passage 2}

\subsection{Words}

\begin{tabular}{lll}
    negligible & adj. & 微不足道的，可忽略的，不重要的 \\
    replenish  & v.   & 补充；把…再备足；重新装满   \\
    depletion  & n.   & 减少；减小；缩小        \\
    philosophy & n.   & 人生哲学;生活（或工作）准则  \\
    scheme     & n.   & 计划              \\
    capillary  & adj. & 毛细管;（尤指）毛细血管    \\
\end{tabular}

\subsection{Collocation}

\begin{tabular}{ll}
    collocation & 中文 \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q13. Insert
    \end{qst}

    \begin{chc}
        But \textbf{even if} uncooperative farmers were to join in the conservation efforts, this would only delay the depletion of the aquifer.
    \end{chc}

    \begin{psgq}
        The reaction of farmers to the inevitable depletion of the Ogallala varies. Many have been attempting to conserve water by irrigating less frequently or by switching to crops that require less water. $\blacksquare$ Others, however, have adopted the philosophy that it is best to use the water while it is still economically profitable to do so and to concentrate on high-value crops such as cotton.   $\blacksquare$ The incentive of the farmers who wish to conserve water is reduced by their knowledge that many of their neighbors are profiting by using great amounts of water, and in the process are drawing down the entire region’s water supplies. $\blacksquare$

        In the face of the upcoming water supply crisis, a number of grandiose schemes have been developed to transport vast quantities of water by canal or pipeline from the Mississippi, the Missouri, or the Arkansas rivers. $\blacksquare$ Unfortunately, the cost of water obtained through any of these schemes would increase pumping costs at least tenfold, making the cost of irrigated agricultural products from the region uncompetitive on the national and international markets.Somewhat more promising have been recent experiments for releasing capillary water (water in the soil) above the water table by injecting compressed air into the ground.Even if this process proves successful, however, it would almost triple water costs. Genetic engineering also may provide a partial solution, as new strains of drought-resistant crops continue to be developed. Whatever the final answer to the water crisis may be, it is evident that within the High Plains, irrigation water will never again be the abundant, inexpensive resource it was during the agricultural boom years of the mid-twentieth century.
    \end{psgq}

    \begin{nlz}
        C 两个决定点，第一个是 uncooperative farmers，那些不合作的农民，根据这个点，A 和 C 是可能的答案，第二个点就是 even if 的让步，既然待插入句说即使那些人愿意合作，正确插入点之前就必须的说那些人不合作，所以 C 是正确答案，而且 A 前后的 many 一句和 other 一句衔接很紧密，不插入句子。
    \end{nlz}
\end{blk}
