\section{TPO 43 Passage 02}

\subsection{Words}

\begin{tabular}{lll}
    gaseous       & adj.  & 含有气体的；像气体的           \\
    semi-         & pref. & 半固体的                 \\
    clay          & n.    & 黏土，陶土                \\
    slope         & n.    & 斜坡                   \\
    nitrogen      & n.    & 氮（气）                 \\
    aquifer       & n.    & 含水土层，地下蓄水层，砂石含水层     \\
    reservoir     & n.    & 水库；蓄水池               \\
    analogous     & adj.  & 相似的；类似的；可比拟的         \\
    quartz        & n.    & 石英                   \\
    segregate     & v.    & （尤指基于种族或性别原因）隔离并区别对待 \\
    controversial & adj.  & 有争议的                 \\
    intensively   & adv.  & 密集地，集中地；加强地；深入地      \\
    squeeze       & v.    & （尤指从各方面）挤压，捏，挤，榨     \\
\end{tabular}

\subsection{Collocation}

\begin{tabular}{ll}
    squeeze sth out of sb & 勒索，敲诈（某人）；逼迫（某人）吐露（信息） \\
\end{tabular}

\newpage

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q6. Why does the author include the information that “\textbf{The force of molecular attraction between oil and quartz or carbonate minerals is weaker than that between water and quartz or carbonate minerals.}”?
    \end{qst}

    \begin{chc}
        A. To help explain why petroleum behaves differently from water in bodies of sandstone and limestone

        C. To help explain how water and petroleum can mix in certain aquifers
    \end{chc}

    \begin{psgq}
        \textbf{The force of molecular attraction between oil and quartz or carbonate minerals is weaker than that between water and quartz or carbonate minerals.} \ul{\textbf{Hence}, because oil and water do not mix, water remains fastened to the quartz or carbonate grains, while oil occupies the central parts of the larger openings in the porous sandstone or limestone.} Because oil is lighter than water, it tends to glide upward past the carbonate- and quartz-held water. In this way, oil becomes segregated from the water; when it encounters a trap, it can form a pool.
    \end{psgq}

    \begin{nlz}
        分子之间的吸引力在石油和石英、碳酸盐矿物之间是弱于水和石英、碳酸盐矿物的。A选项与内容相符。
    \end{nlz}
\end{blk}

\newpage