\section{TPO 45 Passage 02}

\subsection{Words}

\begin{tabular}{lll}
    respectively & adv.   & 分别地（依次）   \\
    interfere    & v.     & 干涉        \\
    impediment   & n.     & 障碍        \\
    primitive    & adj.n. & 原始的；原始派画家 \\
    solitary     & adj.   & 单独的       \\
    dispense     & v.     & 分配；分发     \\
    deciduous    & adj.   & 落叶的       \\
    stigmas      & n.     & 耻辱；柱头     \\
    allergy      & 过敏症；厌恶             \\
    snatch       & v.     & 夺走        \\
\end{tabular}

\subsection{Collocation}

\begin{tabular}{ll}
    interfere with & 干预；干扰 \\
\end{tabular}

\newpage

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q4. Paragraph 1 supports which of the following as the reason \textbf{animals are a safer bet than wind} as \textbf{pollinators when the individual trees of a species are widely separated}?
    \end{qst}

    \begin{chc}
        A. Animals tend to carry pollen from a given flower further than the wind does.

        C. An animal that visits a flower is likely to deliberately visit other flowers of the same species and pollinate them.
    \end{chc}

    \begin{psgq}
        For the relatively few dominant tree species that make up temperate forests, where there are many individuals of \textbf{the same species} within pollen range, this is quite a \textbf{safe gamble}.
    \end{psgq}

    \begin{nlz}
        C选项意为光顾某一种花的animals很有可能会光顾同一种花的另外一朵花并对其授粉。这完全可以构成题干的观点成立的理由之一。 A选项的further的说法无依据。 B选项并不能表明题干的safer的理由。 D选项的fly in all directions的说法无中生有。
    \end{nlz}
\end{blk}

\begin{blk}
    \begin{qst}
        Q6. Paragraph 2 suggests that wind-pollinated plants do not have bright petals, nectar, and scent for which TWO of the following reasons? To receive credit, you must select TWO answers.
    \end{qst}

    \begin{chc}
        A. They \textbf{interfere with} pollination by wind.

        C. They are \textbf{unnecessary}.

        D. They reduce the amount of pollen that can be produced.
    \end{chc}

    \begin{psgq}
        Since wind-pollinated flowers have \textbf{no need} to attract insects or other animals, they have dispensed with bright petals, nectar, and scent. These are at best a waste and at worst an \textbf{impediment} to the transfer of pollen in the air. The result is insignificant-looking flowers and catkins (dense cylindrical clusters of small, petalless flowers).
    \end{psgq}

    \begin{nlz}
        A选项的interfere with对应原文中的impediment。 C选项的unnecessary对应原文的no need.
    \end{nlz}
\end{blk}

\newpage