\section{TPO 51 Passage 03}

\subsection{Words}

\begin{tabular}{lll}
    surge        & n. & 陡增，剧增，急剧上升 \\
    famine       & n. & 饥荒         \\
    malnutrition & n. & 营养不良       \\
    remediation  & n. & 补救；矫正，纠正   \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q1. According to paragraph 1, which of the following is true about Europe in the nineteenth century?
    \end{qst}

    \begin{chc}
        A. A large increase in food production led to industrialization.

        B. Population changes occurred at the same pace in the major regions.

        C. The standard of living rose to the level of that in most parts of the world.

        D. The tremendous rise in population led to greater agricultural output in every region.
    \end{chc}

    \begin{psgq}
        Because of industrialization, but also because of \textbf{a vast increase in agricultural output without which industrialization would have been impossible}, Western Europeans by the latter half of the nineteenth century enjoyed higher standards of living and longer, healthier lives than most of the world’s peoples. In Europe as a whole, the population rose from 188 million in 1800 to 400 million in 1900. By 1900, virtually every area of Europe had contributed to the tremendous surge of population, but each major region was at a different stage of demographic change.
    \end{psgq}

    \begin{nlz}
        本题为事实信息题。题目问：关于19世纪的欧洲下面哪一项是正确的？

        A选项：食物产量的增长导致了工业化。正确，因为第一段第一句话中说“a vast increase in agricultural output without which industrialization would have been impossible”，说明农业产出是工业化的先决条件，故A选项为正确答案。

        B选项：主要地区的人口变化节奏一致。错误，对应第一段最后一句中说的“but each major region was at a different stage of demographic change”，所以B选项与原文完全矛盾，排除。

        C选项：生活水平提高到和世界其他地方一样的水平。错误，对应第一段第一句话中说的“Western Europeans by the latter half of the nineteenth century enjoyed higher standards of living and longer, healthier lives than most of the world’s peoples.”通过这个比较级可以明显看出欧洲人民的生活水平更高，故C排除。

        D选项：人口的大量增长导致了各个地区农业产值的增长。根据第一段内容可知，是农业的发展，推动了人口增长。故D选项逻辑颠倒。排除。所以本题选A.
    \end{nlz}
\end{blk}
