\section{TPO 6 Passage 1}

\subsection{Words}

\begin{tabular}{lll}
    harness & v. & 控制；利用…的动力 \\
    textile & n. & 纺织物；织物    \\
\end{tabular}

\subsection{Analyse}

\begin{blk}
    \begin{qst}
        Q11.According to paragraph 4, providing a machine to take the place of the horse involved combining which two previously separate ingredients?
    \end{qst}

    \begin{chc}
        B. Stationary steam engines and wagons with flanged wheels

        C. Metal rails in roadbeds and wagons capable of carrying heavy loads
    \end{chc}

    \begin{psgq}
        By 1800 more than a thousand steam engines were in use in the British Isles, and Britain retained a virtual monopoly on steam engine production until the 1830s. Steam power did not merely spin cotton and roll iron; early in the new century, it also multiplied ten times over the amount of paper that a single worker could produce in a day. At the same time, operators of the first printing presses run by steam rather than by hand found it possible to produce a thousand pages in an hour rather than thirty. Steam also promised to eliminate a transportation problem not fully solved by either canal boats or turnpikes. Boats could carry heavy weights, but canals could not cross hilly terrain; turnpikes could cross the hills, but the roadbeds could not stand up under great weights. These problems needed still another solution, and the ingredients for it lay close at hand. In some industrial regions, heavily laden wagons, with flanged wheels, were being hauled by horses along metal rails; and the stationary steam engine was puffing in the factory and mine. Another generation passed before inventors succeeded in combining these ingredients, by putting the engine on wheels and the wheels on the rails, so as to provide a machine to take the place of the horse. Thus the railroad age sprang from what had already happened in the eighteenth century.
    \end{psgq}

    \begin{nlz}
        以 ingredients 做关键词定位至倒数第二句，有 combining these ingredients：Another generation passed before inventors succeeded in combining these ingredients, by putting the engine on wheels and the wheels on the rails, so as to provide a machine to take the place of the horse.这句话 by 后面就提到了两个事物就是 wheel 和 engine。如果还不确定的话，可以往前看一句，these 说明答案在前句。前句分别说到蒸汽机和马车，所以答案是 B。
    \end{nlz}
\end{blk}

\begin{blk}
    \begin{qst}
        Q14
    \end{qst}

    \begin{chc}
        A.In the early eighteenth century, Savery and Newcomen discovered that expanding steam could be used to raise a piston in a cylinder.

        F.The availability of steam engines was a major factor in the development of railroads, which solved a major transportation problem.
    \end{chc}

    \begin{nlz}
        BDF in the early 选项是第二段中的一个细节，不选。Watt’s steam engine 选项对应原文第三段第一句，或者说整个第三段，正确。Until 选项对应第四段第一句，但这句话 不是中心句，所以是细节，不选。In the mid 选项对应原文第二段后三句，正确。in the 1790s 选项是第三段中的一个细节，不选。the availability 选项对应原文第四段后三句，正确。
    \end{nlz}
\end{blk}