\section{TPO 30}

\subsection{Example}

In the reading material, the author raises three strong arguments to cast doubt on the existence of “burning mirror” in ancient Greek port city. However the lecturer states that the burning mirror might have once appeared in history by reputing the writer’s arguments one by one.

First, the author argues that it was technologically impossible to build such a tremendous mirror by a single sheet of copper in ancient Greece. Yet the speaker shows by \textbf{experiment that dozens of small polished copper may do the same job efficiently} and Greek \textbf{mathematicians} were excellent enough to accomplish it perfectly.

Besides, in view of the author, it might take a long time for the burning mirror to set a wooden ship on fire \textbf{and the enemy wouldn’t be stupid to stay still for ten minutes. The lecturer, however, points out those ancient warships were not built by wood only.} A special material called pitch was used to fill the spaces between and pitch catches fire quickly. \textbf{Thus it was possible for a burning mirror to burn the pitch first then the ship. In this way can a burning mirror be an effective weapon.}

Lastly, the author argues that the burning mirror is less effective and flexible than flaming arrows. \textbf{Thus ancient Greek won’t bother to devote much effort to build such a useless weapon. }Nonetheless, the lecturer argues that since flaming arrows are usual weapons used so much, Roman soldiers were \textbf{familiar with them and knew how to protect the ship from burning by flaming arrows.} But on the other hand, it was extremely hard to predict where the burning mirror would fire the ship. Thus it is more effective to use a burning mirror than flaming arrows.

\subsection{Integrated Writing}

\begin{quote}
    In the reading section, the author holds the view that the burning mirror should not be an actual weapon with which Greek port city defend themselves from the Roman's attack.However, the speaker disagree with this idea and disprove it mainly with three points.
\end{quote}

In the reading material, the author cast doubt on the existence of burning mirror in ancient Greek port city. However, the professor in the listening argues that none of these reasons are convicing.

\begin{quote}
    To begin with, the author hold the point that the Greek haven't the technology to build mirror.<<< However, the speaker says that they don't have to build such a mirror that is about several meters wide. On the contrary, they only need to build the single sheet mirror. Instead, they can add small individual mirrors together into a sheet so that they can make a multi-sheet mirror, which can work as the same fuction.
\end{quote}

The first reason mentioned by the author is that it is technologically impossible to build such a tremendous mirror using a single sheet of copper in ancient Greece. Yet the professor argues that experiment shows it is possible to use donzens of small copper to do the same job effeciently. Thus Greek didn't need to create a precise large mirror at all. In this way, their technology were just enough to reach this achievement with the help of mathmetics.

\begin{quote}
    Moreover, the author point out that it takes about 10 minutes to set a fire on a wooden boat 30 meters away.<<< But the fact is that they don't need to fire the wooden materials. In fact, they only need to set a fire on the pitch, which is much easier to fire, only taking seconds.<<So
\end{quote}

The second reason mentioned by the author is that it takes about ten minutes for the burning mirror to set a fire on a wooden ship, and the enermy wouldn't just wait for this. The professor, however, holds that the ancient ships were not built by wood only. On the other hand, pitch, which is a material to make the ships water-proof, catch fire in seconds. In this way, burning mirrors can fire the pitch to burn the whole ship.

\begin{quote}
    Last but not least, the author hold the point that arrows are much effective tools than the burning mirror. However, the speaker point out that arrows are easiler to be found by the enermy. On the contrary, when using the burning mirror. The solders can't see the fire rise. So they are unable to put it off too.
\end{quote}

The third reason mentioned by the author is that flamming arrows are more flexiable and effective than the burning mirror. The professor, in the reading, maintains that since the arrows were usual weapons in the war, the soldiers could easily find them and protect the ship from being burned. But on the other hand, the lights from the mirror can hardly be detected. So it is an effective weapon than the arrows.

\subsection{Integrated Writing 2}

In the reading material, the author cast doubt on the existence of the burning mirror in ancient Greek port cities. However, the professor in the listening argues that none of these reasons are convincing.

The first reason mentioned by the author is that it is technologically impossible to construct such a tremendous mirror using a single sheet of copper in ancient Greece. Yet the professor asserts that trial demonstrates it is possible to utilize dozens of small copper to do the same job efficiently. Thus the Greeks didn't need to create a precise large mirror at all. In this way, their technology was just enough to attain this with the help of mathematics.

The second reason mentioned by the author is that it requires about ten minutes for the burning mirror to set a fire on a wooden ship, and the enemy wouldn't just wait for this. The professor, however, holds that the ancient ships were not built by wood only. On the other hand, pitch, which is a material to make the ships waterproof, catch fire in seconds. In this way, burning mirrors can fire the pitch to burn the entire ship.

The third reason mentioned by the author is that flamming arrows are more flexible and effective than the burning mirror. The professor, in the reading, maintains that since the arrows were usual weapons in the war, the soldiers could effortlessly find them and protect the vessel from being burned. But on the other hand, the lights from the mirror can barely be detected. So it is more effective than the arrows.