新·托福写作2023年7月26日上午场 科技媒体-购物建议（Medium）

In my point of view, I will choose the first option. To begin with, I am unwilling to be influenced by internet suggestions. Since we all know internet suggestions are always given for the profit of shops. And the shop advertise their goods mainly for their profit. It is apparently that the quality of the internet suggestions are not reliable. So on the other hand, it is a natural idea to buy only the products advised by our parents or friend. The quality of these goods is always good because they are tested by themselves. Moreover, the guildence of parents or close friends is always detailed and trust-worse. As an result, we can talk to them for even more details about the products. So we can know more about the goods in this way.


新·托福写作2023年7月26日下午场 科技媒体-社交媒体的影响（Hard）

In my point of view, influencers have a positive impact on their followers. To start with, the influencers are not only a ideal model for the followers, but also an internal movivation for them. Take myself as an example, when I heard from Tan, who is a famous programer in Microsoft, will share his opinion in a lecture in my school. I was really excited. And he also taught us about his living habits, which is really helpful for the programers. And as a result, I was really impressed by him and in the following months, I take him as a idol and study like him in my own life too. That means, on the other hand, his skills and habits are also nessisary for in everyday life. Therefor, I support the idea that influencers have brilliant effect on the followers.


In my point of view, while influencers may have some negative aspects, I believe their positive impact outweighs the shortcomings. To begin with,


新·托福写作2023年7月30日 环境能源-航空碳排放税（Medium）

Rory presents a convincing argument in favor of not administering a carbon tax.

Admittedly, calculating and regulating a carbon tax is really a harsh mean to restore the global warming.

However, considering the extra money, which can do more things to protect the environment, gaining from the tax,I am inclined to prioritize the regulation of a tax counting the carbon release of the airlines.

In my point of view, the tax can not only force the companies to enhance their technology to produce less warm house gases, but also provide government with abundant funds to transform the carbon dioxide which already exists in the air to oxygen and water using chemical changes.

For instance, as the technology has been boosting, a machine which can change the gases from the electricity factory, which are mostly carbon dioxide, can be really necessary to lower the carbon level in Shanghai.

Therefore, I firmly believe that a carbon tax will be helpful to the protection of the environment.

新·托福写作2023年7月31日 环境能源-汽油涨价（Medium）

Amy presents a convincing argument in favor of the policy of increasing the tax on car fuels.

Admittedly, raising the tax can force some people to use public trasportation such as underground instead.

However, considering the people who must use their private cars in their everydady life, the boosting of the price of car fuels will really be a obstuction to have a high quality life for the additional cost of their incoming.

In my point of view, the government should not release a tax on car fuels, and they can use other methods such as releasing more electric cars.

For instance, if there are more electric cars which didn't use fuels and use electricity instead, proor people will be more willing to change to these cars instead.

Therefore, I firmly believe that government should not increase the car fuels tax.

新·托福写作2023年7月31日 信息可靠性（Hard）

Rocy presents a convincing argument that we should use critical thoughts on justifying whether the information on the Internet is true or false.

Admittedly, thinking of the purpose of the resources can help us while determining.

However, considering it can not really tell us whether this is false, we should use other means to reach our goal.

In my point of view, we should look for some more objective resources and the point which has been reaching the agreement.

For instance, when I am looking for how to slove some problems with my Linux operating system, named Arch Linux, I prefer the answer on Arch Linux WIKI, which can be edited and approved by many people, which means if the information is wrong, other people will adjust it.

Therefore, I firmly believe that we should use the official information resources or the information on WIKI.

新·托福写作2023年8月2日 无车中心区（Medium）

Amy presents a convincing argument in favor of making the central zones of the city car-free.

Admittedly, the air in the city center without cars might be cleaner.

However, considering the inconvenience of people who live in the city center, the problem caused by a car-free road will outweigh its benefit.

In my point of view, the actual role of the roads in a city is to let cars driving. And we should not leave the roads just because of the purpose of improving the quality of the air.

For instance, without the function of a car road, we should use underground or bus to go to work or study. If everyone in a city use this, the stations will be crowded with people too. In this way, the traffic cannot afford so many people and will break out in the end.

Therefore, I firmly believe that we should not make the center zones of the city car-free.

新·托福写作2023年8月6日 孩子使用手机的限制（Medium）

Rocy presents a convincinng argument in favor of allowing the usage of the mobile phones for the children.

Admittedly, if students can use the cell phones in their daily life, they will have the ability to contact their parents in time when needed.

However, considering the fact most students might be addicted to the informations on the network, limitation of the moblie phones is a must for the them.

In my point of view, the restriction of the mobile phones can free students from the fake information and the too much games.

For instance, short videos always induce a cost of time for students. They will spend their precious hours in a variety of short-term entertainment in weekend. In this way, they will have no time studying and doing their homework.

Therefore, I firmly believe that the cell phones should be limited to the students.

2023年8月8日 科技媒体-广告策略（Medium）

Rory presents a convincing arugment in favor of the usage of celebrities.

Admittedly, a famous person such as a actor might leave the people who have seen the advertisement a deep impression.

However, considering the fact that it will be a enormous cost to use even an image of the well-known persons, the small company cannot afford it.

In my point of view, the most effective stratgy is to employee apply ordinary people to the advertisement.

For instance, the price of the advertisement of the HuGe, who is a famous actor, is more than 1000 million dollars, and the quantity is ever boosting nowadays.

On the other hand, if we use ordinary people, we can spend most money on paying for the advertisement materials, such as the newspaper, which will be a more effective way to be conside.

Therefore, I firmly believe that we should use ordinary people for advertising.

2023年8月9日 学校教授软技能（Medium）

Amy presents a convincing argument in favor of classes teaching soft-nonacademic skills.

Admittedly, these classes might improve students' capability while working, making them more flexible to start their careers.

However, considering the fact that the soft skills are always updating, it is merely impossible for teachers to meet the needs of students when they graduate from schools.

In my point of view, these nonacademic classes should not be started since they will not be useful for the students.

For instance, the classes in my school did not teach frameworks of programming, for the reason that these frameworks are constantly developing. In this way, even the teachers teachs the latest frameworks, they might be outdated in one year.

Therefore, I firmly believe that the soft skills should not be included in classes.

新·托福写作2023年8月9日 科技媒体-商品评价（Medium）

Amy presents a convincing argument in favor of the online reviews. Admittedly, the online reviews enable use to obtain the capablility to select the products we like. However, considering some negative reviews might induce us not to try ourselves, we might miss some precious experenice in this way. In my point of view, sometimes we should not rely too much on the online reviews, since some fake or not objective comments will decide our decisions. For instance, one day I want to buy surface, which is a easy-to-borrow computer, because it would save lots of weights for me. Unfortunately, a comment confused me a lot, for its poor screen. Although affected by the comment, I finally made my decision to get it. Therefore, in my point of view, we should not rely too much on the online reviews.

